Food-web complexity alters the fitness landscape of an insect herbivore

### 2018-09-21 temporary_morgue/ms_complexity_selection_OLD.Rmd
getting organized

  # subset data for analysis
  filter(phenology == "early", Location == "tree",
         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
  mutate(gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)),
         sc.gall_size = as.numeric(scale(Gall_Height_mm)), 
         sc.clutch_size = as.numeric(scale(gall_individuals)), 
         sc.log.clutch_size = as.numeric(scale(log(gall_individuals))), 
         sc.female_preference = as.numeric(scale(Density_per_100_shoots)),
         sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots))))

## Create separate datasets for quantifying selection gradients ----
control_df <- gall_selection.df %>%
  filter(Treatment.focus == "Control") #%>%
  #mutate(sc.gall_size = as.numeric(scale(Gall_Height_mm)), 
  #       sc.clutch_size = as.numeric(scale(gall_individuals)), 
  #       sc.log.clutch_size = as.numeric(scale(log(gall_individuals))), 
  #       sc.female_preference = as.numeric(scale(Density_per_100_shoots)),
  #       sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots))))

treatment_df <- gall_selection.df %>%
  filter(Treatment.focus == "Ectoparasitoid exclusion", ectos < 1) #%>%  # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
  #mutate(sc.gall_size = as.numeric(scale(Gall_Height_mm)), 
  #       sc.clutch_size = as.numeric(scale(gall_individuals)), 
  #       sc.log.clutch_size = as.numeric(scale(log(gall_individuals))), 
  #       sc.female_preference = as.numeric(scale(Density_per_100_shoots)),
  #       sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots))))

@@

## Calculate selection gradients following method of Janzen and Stern 1998, Evolution
Beta_avg_grad <- function(.) {
  mean_fitness <- mean(predict(., type = "response")) #inverse_logit(fixef(update(., .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
  brackets <- predict(., type = "response") * (1 - predict(., type="response"))
  mean(brackets) * fixef(.)[-1] / mean_fitness 
}

@@

<!-- > *There is a much more insidious kind of extinction: the extinction of ecological interactions.* 
> *(Janzen, D.H. 1974. The deflowering of Central America. Natural History. 83:48–53).* -->

@@

>>>>

  # subset data for analysis
  filter(phenology == "early", Location == "tree",
         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
  filter(Treatment.focus == "Ectoparasitoid exclusion" & ectos < 1 | Treatment.focus == "Control") %>% # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
  mutate(gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)),
         sc.gall_size = as.numeric(scale(Gall_Height_mm)), 
         sc.clutch_size = as.numeric(scale(gall_individuals)), 
         sc.log.clutch_size = as.numeric(scale(log(gall_individuals))), 
         sc.female_preference = as.numeric(scale(Density_per_100_shoots)),
         sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots)))) 
dim(gall_selection.df)

## Create separate datasets for quantifying selection gradients ----
control_df <- gall_selection.df %>%
  filter(Treatment.focus == "Control") #%>%
  #mutate(sc.gall_size = as.numeric(scale(Gall_Height_mm)), 
  #       sc.clutch_size = as.numeric(scale(gall_individuals)), 
  #       sc.log.clutch_size = as.numeric(scale(log(gall_individuals))), 
  #       sc.female_preference = as.numeric(scale(Density_per_100_shoots)),
  #       sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots))))
dim(control_df)

treatment_df <- gall_selection.df %>%
  filter(Treatment.focus == "Ectoparasitoid exclusion", ectos < 1) #%>%  # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
dim(treatment_df)
  #mutate(sc.gall_size = as.numeric(scale(Gall_Height_mm)), 
  #       sc.clutch_size = as.numeric(scale(gall_individuals)), 
  #       sc.log.clutch_size = as.numeric(scale(log(gall_individuals))), 
  #       sc.female_preference = as.numeric(scale(Density_per_100_shoots)),
  #       sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots))))

@@

## Calculate selection gradients following method of Janzen and Stern 1998, Evolution
Beta_avg_grad <- function(.) {
  mean_fitness <- mean(predict(., type = "response")) #inverse_logit(fixef(update(., .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
  brackets <- predict(., type = "response") * (1 - predict(., type="response"))
  mean(brackets) * fixef(.)[-1] / mean_fitness ## need to divide by mean fitness to put on relative fitness scale.
}

@@

So what did I learn this morning? I believe I can reliably estimate selection gradients from a full model by taking care in how I transform the data. This means that I use the data from each treatment to actually calculate the selection coefficients on the scale of relative fitness.
```{r}
hist(gall_selection.df$sc.gall_size)
mean(gall_selection.df$sc.gall_size)
sd(gall_selection.df$sc.gall_size)
hist(rnorm(n = length(gall_selection.df$sc.gall_size), mean = 0, sd = 1))
bind_rows(data.frame(phenotype = gall_selection.df$sc.gall_size, type = "real"), data.frame(phenotype = rnorm(n = length(gall_selection.df$sc.gall_size), mean = 0, sd = 1), type="sim")) %>%
  ggplot(., aes(x=phenotype, fill=type)) + geom_density(alpha=0.25) # this is about as normally distributed as can be...

base_glm <- glm(gall_survival ~ sc.gall_size, gall_selection.df, family=binomial(link="logit"))
inverse_logit(coef(base_glm))
mean(gall_selection.df$gall_survival)

main_glm <- glm(gall_survival ~ Treatment.focus + sc.gall_size, gall_selection.df, family=binomial(link="logit"))
summary(main_glm)
inverse_logit(coef(main_glm))
gall_selection.df %>% group_by(Treatment.focus) %>% summarise(mean_fitness = mean(gall_survival))

inter_glm <- glm(gall_survival ~ Treatment.focus*sc.gall_size, gall_selection.df, family=binomial(link="logit"))
summary(inter_glm)

inter_rev_glm <- glm(gall_survival ~ Treatment.focus*sc.gall_size, mutate(gall_selection.df, Treatment.focus=relevel(as.factor(Treatment.focus), ref="Ectoparasitoid exclusion")), family=binomial(link="logit"))
summary(inter_rev_glm)

mean(predict(base_glm, type="response"))
mean(gall_selection.df$gall_survival)

mean(predict(base_glm, type="response")*(1-predict(base_glm, type="response")))*coef(base_glm)/mean(predict(base_glm, type="response"))
mean(predict(main_glm, type="response")*(1-predict(main_glm, type="response")))*coef(main_glm)[3]/0.4551920
mean(predict(inter_glm, type="response")*(1-predict(inter_glm, type="response")))*coef(inter_glm)[3]/0.4551920
mean(predict(inter_glm, type="response")*(1-predict(inter_glm, type="response")))*(coef(inter_glm)[3]+coef(inter_glm)[4])/0.6168385
mean(predict(inter_rev_glm, type="response")*(1-predict(inter_rev_glm, type="response")))*coef(inter_rev_glm)[3]/0.6168385
mean(predict(inter_rev_glm, type="response")*(1-predict(inter_rev_glm, type="response")))*(coef(inter_rev_glm)[3]+coef(inter_rev_glm)[4])/0.4551920

# now one of the questions is, do you use the mean of the "brackets" for the entire distribution, or just for the particular treatment?

mean(control_df$gall_survival)
mean(predict(glm(gall_survival ~ 1, control_df, family=binomial(link="logit")), type="response"))
mean(predict(glmer(gall_survival ~ 1 + (1|Genotype), control_df, family=binomial(link="logit")), type="response"))
mean(predict(glmer(gall_survival ~ 1 + (1|Genotype)+(1|Plant_Position), control_df, family=binomial(link="logit")), type="response"))
mean(predict(glmer(gall_survival ~ 1 + (1|Genotype)+(1|Plant_Position) + (1|Gall_Number), control_df, family=binomial(link="logit")), type="response"))

test_glmer <- glmer(gall_survival ~ Treatment.focus*sc.gall_size + (1|Genotype)+(1|Plant_Position) + (1|Gall_Number), gall_selection.df, family=binomial(link="logit"))
summary(test_glmer)
summary(inter_glm)
mean(predict(test_glmer, newdata=filter(gall_selection.df, Treatment.focus=="Control"), type="response")*(1-predict(test_glmer, newdata=filter(gall_selection.df, Treatment.focus=="Control"), type="response")))*fixef(test_glmer)[3]/mean(predict(test_glmer, newdata=filter(gall_selection.df, Treatment.focus=="Control"), type="response"))
mean(predict(test_glmer, newdata=filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion"), type="response")*(1-predict(test_glmer, newdata=filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion"), type="response")))*(fixef(test_glmer)[3]+fixef(test_glmer)[4])/mean(predict(test_glmer, newdata=filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion"), type="response"))

piecewiseSEM::rsquared(test_glmer)
piecewiseSEM::rsquared(glmer(gall_survival ~ Treatment.focus*sc.gall_size + (1|Genotype), gall_selection.df, family=binomial(link="logit")))

# the exact same, because of my coding structure
summary(glmer(gall_survival ~ 1 + (1|Genotype)+(1|Plant_Position) + (1|Gall_Number), control_df, family=binomial(link="logit")))
summary(glmer(gall_survival ~ 1 + (1|Genotype/Plant_Position/Gall_Number), control_df, family=binomial(link="logit")))
```

@@

```{r Effects of food-web complexity on components of natural selection, cache=TRUE, include=FALSE}

## Fit GLMM
null_glmer <- glmer(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
                         I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) +
                         sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference +
                         sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference +
                           (1|Genotype/Plant_Position/Gall_Number),
                         data = gall_selection.df,
                         family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"), na.action = "na.fail")

foodweb_glmer <- glmer(gall_survival ~ Treatment.focus*(sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
                         I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) +
                         sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference +
                         sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference) +
                           (1|Genotype/Plant_Position/Gall_Number),
                         data = gall_selection.df,
                         family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"), na.action = "na.fail")

## Test for overdispersion
overdisp_fun(null_glmer)    # no evidence
overdisp_fun(foodweb_glmer) # no evidence

## Compare statistical summaries of each model
summary(null_glmer)
summary(foodweb_glmer)

round(cov2cor(vcov(foodweb_glmer)),2)

## Test statistical significance of effects
anova(null_glmer, foodweb_glmer, test = "Chisq") # evidence that food-web treatment alters the components of natural selection

## Use drop1 to parse out which effects are determining the differences in selection between treatments.
drop1(foodweb_glmer, test="Chisq") # marginal effect of food-web treatment on nonlinear selection acting on female preference

drop1(update(foodweb_glmer, .~. -Treatment.focus:I(sc.gall_size^2) -Treatment.focus:I(sc.log.clutch_size^2) -Treatment.focus:I(sc.log1p.female_preference^2) -Treatment.focus:sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference), test="Chisq") # nonlinear selection acting on gall size in complex food web

drop1(update(foodweb_glmer, .~. -Treatment.focus:I(sc.gall_size^2) -Treatment.focus:I(sc.log.clutch_size^2) -Treatment.focus:I(sc.log1p.female_preference^2) -Treatment.focus:sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -I(sc.gall_size^2) -I(sc.log.clutch_size^2) -I(sc.log1p.female_preference^2) -sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -Treatment.focus:sc.gall_size:sc.log.clutch_size -Treatment.focus:sc.gall_size:sc.log1p.female_preference -Treatment.focus:sc.log.clutch_size:sc.log1p.female_preference), test="Chisq") # marginal effect of correlational selection on gall size and clutch size in the complex food web; food-web treatment altered directional selection on clutch size

drop1(update(foodweb_glmer, .~. -Treatment.focus:I(sc.gall_size^2) -Treatment.focus:I(sc.log.clutch_size^2) -Treatment.focus:I(sc.log1p.female_preference^2) -Treatment.focus:sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -I(sc.gall_size^2) -I(sc.log.clutch_size^2) -I(sc.log1p.female_preference^2) -sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -Treatment.focus:sc.gall_size:sc.log.clutch_size -Treatment.focus:sc.gall_size:sc.log1p.female_preference -Treatment.focus:sc.log.clutch_size:sc.log1p.female_preference -sc.gall_size:sc.log.clutch_size -sc.gall_size:sc.log1p.female_preference -sc.log.clutch_size:sc.log1p.female_preference -Treatment.focus:sc.gall_size -Treatment.focus:sc.log.clutch_size -Treatment.focus:sc.log1p.female_preference), test="Chisq") # strong effect of food-web treatment on absolute fitness; directional selection acting on gall size in complex food web; no directional selection acting on clutch size in the complex food web; directional selection acting on female preference in the complex food web.

summary(update(foodweb_glmer, .~. -Treatment.focus:I(sc.gall_size^2) -Treatment.focus:I(sc.log.clutch_size^2) -Treatment.focus:I(sc.log1p.female_preference^2) -Treatment.focus:sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -I(sc.gall_size^2) -I(sc.log.clutch_size^2) -I(sc.log1p.female_preference^2) -sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -Treatment.focus:sc.gall_size:sc.log.clutch_size -Treatment.focus:sc.gall_size:sc.log1p.female_preference -Treatment.focus:sc.log.clutch_size:sc.log1p.female_preference -sc.gall_size:sc.log.clutch_size -sc.gall_size:sc.log1p.female_preference -sc.log.clutch_size:sc.log1p.female_preference -Treatment.focus:sc.gall_size -Treatment.focus:sc.log.clutch_size -Treatment.focus:sc.log1p.female_preference))
```

It appears that the mixed-effects model qualtiatively alters my conclusions when I compare the results of the full data set to the subset. Why is this? Perhaps it "learns" more from the random effects in the large dataset because it also accounts for the different treatments?
```{r Something funny with mixed effects}
summary(glm(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference, data = treatment_df, family = binomial(link = logit)))
summary(glm(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference, data = control_df, family = binomial(link = logit)))
summary(glm(gall_survival ~ Treatment.focus + sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference, data = gall_selection.df, family = binomial(link = logit)))
summary(glm(gall_survival ~ Treatment.focus*(sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference), data = gall_selection.df, family = binomial(link = logit)))

control_test <- glm(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference, data = control_df, family = binomial(link = logit))
ggplot(data.frame(resids = resid(control_test), Genotype = control_df$Genotype), aes(x=Genotype, y=resids)) +
  geom_boxplot()
summary(lm(resids ~ Genotype, data.frame(resids = resid(control_test), Genotype = control_df$Genotype)))
anova(lm(resids ~ Genotype, data.frame(resids = resid(control_test), Genotype = control_df$Genotype)))

treatment_test <- glm(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference, data = treatment_df, family = binomial(link = logit))
ggplot(data.frame(resids = resid(treatment_test), Genotype = treatment_df$Genotype), aes(x=Genotype, y=resids)) +
  geom_boxplot()
summary(lm(resids ~ Genotype, data.frame(resids = resid(treatment_test), Genotype = treatment_df$Genotype)))
anova(lm(resids ~ Genotype, data.frame(resids = resid(treatment_test), Genotype = treatment_df$Genotype)))

summary(glmer(gall_survival ~ Treatment.focus + sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + (Treatment.focus|Genotype) + (1|Plant_Position/Gall_Number), data = gall_selection.df, family = binomial(link = logit)))

anova(glmer(gall_survival ~ Treatment.focus + sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + (1|Genotype) + (1|Plant_Position) + (1|Gall_Number), data = gall_selection.df, family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa")),
      glmer(gall_survival ~ Treatment.focus + sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + (1|Plant_Position) + (1|Gall_Number), data = gall_selection.df, family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa")), test="Chisq")

anova(glmer(gall_survival ~ Treatment.focus + sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + (1|Genotype) + (1|Plant_Position) + (1|Gall_Number), data = gall_selection.df, family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa")),
      glmer(gall_survival ~ Treatment.focus + sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + (sc.log1p.female_preference|Genotype) + (1|Plant_Position) + (1|Gall_Number), data = gall_selection.df, family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa")), test="Chisq")

summary(glmer(gall_survival ~ Treatment.focus + sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + (sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference|Genotype) + (1|Plant_Position) + (1|Gall_Number), data = gall_selection.df, family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa")))

summary(glmer(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + (1|Genotype) + (1|Plant_Position/Gall_Number), data = control_df, family = binomial(link = logit)))

with(gall_selection.df, table(Genotype, Treatment.focus))
```

```{r}
foodweb_glm <- glm(gall_survival ~ Treatment.focus*(sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
                         I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) +
                         sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference +
                         sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference),
                         data = gall_selection.df,
                         family = binomial(link = logit), na.action = "na.fail")

## Compare statistical summaries of each model
summary(foodweb_glm)

## Use drop1 to parse out which effects are determining the differences in selection between treatments.
drop1(foodweb_glm, test="Chisq") # marginal effect of food-web treatment on nonlinear selection acting on female preference

drop1(update(foodweb_glm, .~. -Treatment.focus:I(sc.gall_size^2) -Treatment.focus:I(sc.log.clutch_size^2) -Treatment.focus:I(sc.log1p.female_preference^2) -Treatment.focus:sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference), test="Chisq") # nonlinear selection acting on gall size in complex food web

drop1(update(foodweb_glm, .~. -Treatment.focus:I(sc.gall_size^2) -Treatment.focus:I(sc.log.clutch_size^2) -Treatment.focus:I(sc.log1p.female_preference^2) -Treatment.focus:sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -I(sc.gall_size^2) -I(sc.log.clutch_size^2) -I(sc.log1p.female_preference^2) -sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -Treatment.focus:sc.gall_size:sc.log.clutch_size -Treatment.focus:sc.gall_size:sc.log1p.female_preference -Treatment.focus:sc.log.clutch_size:sc.log1p.female_preference), test="Chisq") # marginal effect of correlational selection on gall size and clutch size in the complex food web; food-web treatment altered directional selection on clutch size

drop1(update(foodweb_glm, .~. -Treatment.focus:I(sc.gall_size^2) -Treatment.focus:I(sc.log.clutch_size^2) -Treatment.focus:I(sc.log1p.female_preference^2) -Treatment.focus:sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -I(sc.gall_size^2) -I(sc.log.clutch_size^2) -I(sc.log1p.female_preference^2) -sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -Treatment.focus:sc.gall_size:sc.log.clutch_size -Treatment.focus:sc.gall_size:sc.log1p.female_preference -Treatment.focus:sc.log.clutch_size:sc.log1p.female_preference -sc.gall_size:sc.log.clutch_size -sc.gall_size:sc.log1p.female_preference -sc.log.clutch_size:sc.log1p.female_preference -Treatment.focus:sc.gall_size -Treatment.focus:sc.log.clutch_size -Treatment.focus:sc.log1p.female_preference), test="Chisq") # strong effect of food-web treatment on absolute fitness; directional selection acting on gall size in complex food web; no directional selection acting on clutch size in the complex food web; directional selection acting on female preference in the complex food web.

summary(update(foodweb_glm, .~. -Treatment.focus:I(sc.gall_size^2) -Treatment.focus:I(sc.log.clutch_size^2) -Treatment.focus:I(sc.log1p.female_preference^2) -Treatment.focus:sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -I(sc.gall_size^2) -I(sc.log.clutch_size^2) -I(sc.log1p.female_preference^2) -sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -Treatment.focus:sc.gall_size:sc.log.clutch_size -Treatment.focus:sc.gall_size:sc.log1p.female_preference -Treatment.focus:sc.log.clutch_size:sc.log1p.female_preference -sc.gall_size:sc.log.clutch_size -sc.gall_size:sc.log1p.female_preference -sc.log.clutch_size:sc.log1p.female_preference -Treatment.focus:sc.gall_size -Treatment.focus:sc.log.clutch_size -Treatment.focus:sc.log1p.female_preference))

```{r}
glm_control <- glm(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
                     I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) +
                     sc.gall_size:sc.log.clutch_size + sc.log.clutch_size:sc.log1p.female_preference + sc.gall_size:sc.log1p.female_preference + sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference, data = control_df, family = binomial(link = logit))
drop1(glm_control, test="Chisq")
drop1(update(glm_control, .~. -I(sc.gall_size^2) -I(sc.log.clutch_size^2) -I(sc.log1p.female_preference^2) -sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference), test="Chisq")
drop1(update(glm_control, .~. -I(sc.gall_size^2) -I(sc.log.clutch_size^2) -I(sc.log1p.female_preference^2) -sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -sc.gall_size:sc.log.clutch_size -sc.log.clutch_size:sc.log1p.female_preference -sc.gall_size:sc.log1p.female_preference), test="Chisq")

glm_treatment <- glm(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
                     I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) +
                     sc.gall_size:sc.log.clutch_size + sc.log.clutch_size:sc.log1p.female_preference + sc.gall_size:sc.log1p.female_preference + sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference, data = treatment_df, family = binomial(link = logit))
drop1(glm_treatment, test="Chisq")
drop1(update(glm_treatment, .~. -I(sc.gall_size^2) -I(sc.log.clutch_size^2) -I(sc.log1p.female_preference^2) -sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference), test="Chisq")
drop1(update(glm_treatment, .~. -I(sc.gall_size^2) -I(sc.log.clutch_size^2) -I(sc.log1p.female_preference^2) -sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -sc.gall_size:sc.log.clutch_size -sc.log.clutch_size:sc.log1p.female_preference -sc.gall_size:sc.log1p.female_preference), test="Chisq")
```
